Are We Teaching Cybersecurity (and how well)?\\(Abstract 20 January, Paper 27th)

### 2019-01-03 ITiCSE2019.tex
Add files via upload
added "what does the BCS tell Universities" and "Accreditation - what progress has been made"

\subsection{What does BCS tell Universities}
and what happens.  {\bf Action TP}.

@@

{\bf JHD to ? Poll CPHC, and/or survey job adverts.}
\subsection{Accreditation}
?AI/TP to write something.

@@

The agreed Cybersecurity Principles and Learning Outcomes were included in the BCS Guidelines for accreditation in 2016. This resulted in an extended expectation of the coverage of Cybersecurity in programmes accredited by the Institute. The expectation is now that all students upon all accredited programmes will graduate with skills, knowledge and experience related to:
\begin{enumerate}
\item Information and risk
\item Threats and attacks
\item Cybersecurity architecture and operations
\item Secure systems and products
\item Cybersecurity management
\end{enumerate}
This was discussed with the wider education community by a road-show lead by CPHC. (Alastair could you add something here?)

This change to the accreditation guidelines is now in an implementation period. The accreditation process adopted by the BCS is cyclic in nature. Formally the cycle is 5 years in duration. The new expectations have been implemented as follows. To ensure continuous accreditation,  accreditation visits are normally scheduled every 5 years. At the time of the next visit in this accreditation cycle accreditation is conditional upon a HEI having considered the guidelines and either adjusted the curriculum to meet the new expectations or have a formal plan in place for when and how adjustments will be made.  It is anticipate from 2020(?) the expectation will be all accredited programmes have the new expectations fully embedded.

TO DO - Has this worked? Should we ask the BCS accreditation team a favour to see if they will let us know: 
1. Total number of accredited programmes
2. impact of changes to  BCS Accreditation Cybersecurity requirements - maybe number of HEIs with a 90 day related to it or possibly number with "At Threshold"
3. Would this give us enough evidence of some impact? Clearly it is a work in progress but I think some progress has been made?
4. Any things else?

>>>>

@@

{\bf JHD to ? Poll CPHC, and/or survey job adverts.}
\subsection{Accreditation}
{\bf{Alastair could you check this and adjust if appropriate?}}

@@

The agreed Cybersecurity Principles and Learning Outcomes were included in the BCS Guidelines for accreditation in 2015. This resulted in an extended expectation of the coverage of Cybersecurity in programmes accredited by the Institute. The expectation is now that all students upon all accredited programmes will graduate with skills, knowledge and experience related to:
\begin{enumerate}
\item Information and risk
\item Threats and attacks
\item Cybersecurity architecture and operations
\item Secure systems and products
\item Cybersecurity management
\end{enumerate}

\subsection{What does BCS tell Universities}
The agreed Cybersecurity Principles and Learning Outcome were discussed with the wider education community by a road-show lead by CPHC. {\bf{(Alastair could you add something here?)}}

The BCS Guidelines on Course Accreditation are published upon the BCS website \cite{BCS2018a}. The BCS also publishes the changes that have been made \cite{BCS2018b}. When changes are made, the BCS communicates the changes by email and in writing to all the BCS Educational Affiliates, that is all the HEIs that seek accreditation from the BCS. The expectations for Cybersecurity were extended in the June 2015 version of the guidelines for consideration at Accreditation Visits that took place from September 2015 or later.

This change to the accreditation guidelines is now in an implementation period. The accreditation process adopted by the BCS is cyclic in nature. Formally, the cycle is 5 years in duration. The new expectations have been implemented as follows. To ensure continuous accreditation, accreditation visits are normally scheduled every 5 years. At the time of the next visit in this accreditation cycle, accreditation is conditional upon a HEI having considered the guidelines and either adjusted the curriculum to meet the new expectations or have a formal plan in place for when and how adjustments will be made.  It is anticipated that from 2020(?) the expectation will be all accredited programmes have the new expectations fully embedded.

In the year prior to an Accreditation Visit, HEIs are invited to an Accreditation Briefing from the BCS. The intention of the briefing is to help ensure Accreditation Visits go smoothly from the perspective of both the BCS and visited HEI. The briefings take place virtually. The briefing includes a summary of the process, discussion of recent changes, guidance regarding the application and a summary of common issues that are being seen in other HEIs. Significant opportunity for seeking clarification is provided. One of the issues that is highlighted is not all institutions have yet evolved their programmes to fully address the increased expectation for Cybersecurity. This is resulting in accreditation being contingent upon a HEI taking action to address this short fall or in some cases the withdrawal of accreditation. A number of HEIs are in the process of adjusting their curricula to meet the new expectations. In this case, the BCS notes the changes to programme design, the outputs from which will be scrutinized at the next accreditation visit.

\subsection{Accreditation - what progress has been made}

This initiative is a collective attempt to formally include Cybersecurity in all BCS Accredited programmes. Some of these programmes will be specialist Cybersecurity programmes, however the majority will take a different emphasis. This is a work in progress. A full cycle of accreditation visits has not yet taken place following the adjustment to the BCS Guidelines. What is being observed is the majority of visited HEIs have now either adjusted their curricula to extend the coverage of Cybersecurity or have a plan in place to do so. However, a minority are requiring encouragement to do so.

{\bf {
TO DO

TP made information request on 03/01/19. Education team are on holiday to 7/01/19. They also are currently short staffed.

What I have requested is:

1.	The HEIs / number of programmes we have refused accreditation on the basis of Cybersecurity
2.	The number of HEIs / programmes which we have requested a 90 day or an action plan on the basis of Cybersecurity ( that was then successfully addressed)
3.	The number of HEIs / programme which are marked “At Threshold” for Cyber Security

This clearly may or may not be forthcoming.

}}
